---
title: "UFC in 2019"
author: "Atilla Serkan Savas"
date: "18 07 2020"
output:
  html_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE
)
```

# UFC in 2019 

As a casual UFC fan, I just wanted to visualize UFC in 2019. I just wanted to focus on one topic, maybe next time I will try to do something more general. I hope you like it, I would appreciate it if you upvote and give me some feedback.


# Packages

```{r}
library(ggcharts)
library(tidyverse)
library(lubridate)
```

```{r}
data = read.csv("C:\\Users\\atill\\Desktop\\datasets\\data.csv")

```

## Filtering the data

```{r}
data$date <- lubridate::as_date(data$date)
data$year <- lubridate::year(data$date)
data_2019 <- data %>%
  filter(year == 2019)
```

# Charts

```{r}

lollipop_chart(data_2019, Referee , top_n = 15 ,point_color = "#d44446", line_color = "#a08070") 

```
Congrats Marc Goddard!


```{r}
lollipop_chart(data_2019, weight_class ,point_color = "#d44446", line_color = "#a08070") 
```
Lightweight at the top. Not surpising, it is the most popular division in UFC.

```{r}
lollipop_chart(data_2019, title_bout , top_n = 10 ,point_color = "#d44446", line_color = "#a08070") 

```

```{r}
table(data_2019$title_bout)

```

Only 8 title fights took place in 2019.

```{r}
bar_chart(data_2019, title_bout, facet = weight_class) 

```


```{r}
table(data_2019$title_bout,data_2019$weight_class)

```






```{r}
total_stance <- c(data_2019$R_Stance,data_2019$B_Stance)
total_stance <- as.data.frame(total_stance)
total_stance$total_stance[total_stance$total_stance == ""] <- "open stance"
total_stance %>%
  lollipop_chart(total_stance  ,point_color = "#d44446", line_color = "#a08070") 
```

```{r}
  lollipop_chart(data_2019, no_of_rounds  ,point_color = "#d44446", line_color = "#a08070") 

```
```{r}
table(data_2019$Winner)
```

